SS finding report

### 2021-11-26 experiments/0_ss_finding/report.Rmd
various

---
title: "SS finding report"
author: "Owen Petchey"
date: "11/25/2021"
output: html_document
---

```{r}
library(microxanox)
library(tidyverse)

@@

```{r}
plot_ss_result3(ss_9s, 1)
plot_ss_result3(ss_9s, 2)
plot_ss_result4(ss_9s, 1, 2)
```

>>>>

---
title: "SS finding report"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r echo = FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
library(microxanox)
library(tidyverse)
library(patchwork)
library(here)

@@

```{r}
plot_ss_result3(ss_9s, 1)
plot_ss_result3(ss_9s, 8)
plot_ss_result4(ss_9s, 1, 8)
```
